A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus \\ (Draft)

### 2014-08-25 Papers/NaturalDeduction/GodProof-ND.tex
Add ToDo

@@

@@

@@

\setcounter{axiom}{0}

@@

>>>>

ToDo: Talk about constant domains and varying domains, mention Conchiarella's semantics and Anderson's footnote 14.

@@

\setcounter{axiom}{0}
\setcounter{lemma}{0}
\setcounter{theorem}{0}
\setcounter{corollary}{0}

ToDo: natural language explanation of the proof in Anderson.

@@

\setcounter{axiom}{0}
\setcounter{lemma}{0}
\setcounter{theorem}{0}
\setcounter{corollary}{0}

@@

@@

Anderson's footnote 5 on KB

ToDo: talk about anderson's footnote 2, where he argues that an anonymous referee knew the simpler proof of T1.

Hajek (magari and others) on non-provability of ex x. G(x) in KD45.
